\documentclass{article}

\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\usepackage{graphicx}

\usepackage{tcolorbox}

\usepackage{tikz}

% from https://tex.stackexchange.com/a/36607/207458
\newcommand{\AxisRotator}[1][rotate=0]{%
  \tikz [x=0.25cm,y=0.60cm,line width=.2ex,-stealth,#1] \draw (0,0) arc (-150:150:1 and 1);%
}


% from https://tex.stackexchange.com/a/21957/207458
\usetikzlibrary{decorations}

\pgfdeclaredecoration{triangle}{start}{
  \state{start}[width=0.99\pgfdecoratedinputsegmentremainingdistance,next state=up from center]
  {\pgfpathlineto{\pgfpointorigin}}
  \state{up from center}[next state=do nothing]
  {
    \pgfpathlineto{\pgfqpoint{\pgfdecoratedinputsegmentremainingdistance}{\pgfdecorationsegmentamplitude}}
    \pgfpathlineto{\pgfqpoint{\pgfdecoratedinputsegmentremainingdistance}{-\pgfdecorationsegmentamplitude}}
    \pgfpathlineto{\pgfpointdecoratedpathfirst}
  }
  \state{do nothing}[width=\pgfdecorationsegmentlength,next state=do nothing]{
    \pgfpathlineto{\pgfpointdecoratedinputsegmentfirst}
    \pgfpathmoveto{\pgfpointdecoratedinputsegmentlast}
  }
}

\tikzset{
  triangle path/.style={decoration={triangle,amplitude=#1}, decorate},
  triangle path/.default=1ex
}

\usepackage{listings}
\lstset{
  basicstyle=\ttfamily\small,
  breaklines=true,
  frame=single
}
\usepackage{physics}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}
\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  filecolor=magenta,
  urlcolor=cyan,
  pdftitle={INTDER Manual},
  pdfpagemode=FullScreen,
}

\newcommand\e[1]{$\times 10^{#1}$}

\title{Rust INTDER Manual}
\date{}
\author{Brent R. Westbrook}

\begin{document}

\maketitle

INTDER is a program for performing coordinate transformations between
simple-/symmetry-internal coordinates and Cartesian coordinates. It was
originally written in Fortran by Wesley D. Allen and coworkers but has since
been translated to Rust by Brent R. Westbrook. This documentation corresponds to
the Rust version only.

\section{Internal Coordinates}
\label{sec:coords}

At their most basic, internal coordinates are those defined with reference to
other atoms in the same molecule (or system), as opposed to an external set of
axes or some other frame of reference. Simple examples of internal coordinates
are distances between pairs of atoms and angles between sets of three atoms. A
major benefit of using internal coordinates over an external coordinate system
like Cartesian coordinates is that internal coordinates require only 3$N-6$ (or
3$N-5$ for linear molecules) coordinates to describe a system fully since the 3
translational and 3 rotational degrees of freedom only have meaning in an
external reference frame. $N$ in this case is, of course, the number of atoms in
the system. Given the exponential scaling of the number of points required to
describe a quartic force field (QFF), or really any potential energy surface
(PES), with the number atoms, this difference of 6 coordinates can have a large
effect. As a result, using internal coordinates can lead to a substantial
decrease in computational cost for such a PES.

\subsection{Simple-Internal Coordinates}
\label{sec:simple}

Simple-internal coordinates are the basic building blocks of symmetry-internal
coordinates, the major focus of the rest of the manual. The types of
simple-internal coordinates supported by INTDER are described in the following
subsections.

\subsubsection{Stretch}
\label{sec:stretch}

The bond stretch, referred to as \verb|STRE| in the input file, is the distance
between two atoms, as shown in Fig.~\ref{fig:stre}. When the direction matters,
the distance is computed from atom \verb|A| to atom \verb|B|, using the equation
given in Eqn.~\ref{eq:stre}, where $a_i$ and $b_i$ represent the $i$th
components of the Cartesian coordinates of atoms \verb|A| and \verb|B|,
respectively.

\begin{figure}[ht]
  \centering
  \caption{A stretch}
  \label{fig:stre}

  \begin{tikzpicture}
    \node[draw,circle] (A) at (0,0) {A};
    \node[draw,circle] (B) at (2,0) {B};
    \draw[thick, ->] (A) to (B);
    \draw[thick] (A) -- (B) node[midway, above] {$r$};
  \end{tikzpicture}
\end{figure}

\begin{equation}
  \label{eq:stre}
  r = \sqrt{\sum_i (b_i - a_i)^2}
\end{equation}

\subsubsection{Bend}
\label{sec:bend}

The bend, referred to as \verb|BEND| in the input file, is the angle between
three atoms, as shown in Fig.~\ref{fig:bend}.

\begin{figure}[ht]
  \centering
  \caption{A bend}
  \label{fig:bend}

  \begin{tikzpicture}
    \node[draw,circle] (A) at (0,0) {A};
    \node[draw,circle] (B) at (2,0) {B};
    \node[draw,circle] (C) at (3,-2) {C};
    \draw[thick] (A) -- (B) node[midway] (m) {};
    \draw[thick] (B) -- (C) node[midway] (n) {};
    \path (m) edge [bend left=-90] node[below] {$\theta$} (n);
    \draw[thick, ->] (B) -- (m) node[midway, above] {$\vec{e}_{BA}$};
    \draw[thick, ->] (B) -- (n) node[midway, above right] {$\vec{e}_{BC}$};
  \end{tikzpicture}
\end{figure}

The value of the angle, $\theta$ is computed using Eqn.~\ref{eq:bend}, where
$\vec{e}_{ij}$ represents the unit vector pointing from atom $i$ to atom $j$.

\begin{equation}
  \label{eq:bend}
  \theta = \acos(\vec{e}_{BA} \cdot \vec{e}_{BC})
\end{equation}

\subsubsection{Linear bend}
\label{sec:lin1}

The linear angle bend, referred to as \verb|LIN1| in the input file, is similar
to a regular bend, but atoms \verb|A|, \verb|B|, and \verb|C| are in a line, so
specifying the angle between them requires a fourth atom, \verb|D|, which must
be a dummy atom specified at the end of the geometry. Typically the coordinates
of \verb|D| are chosen to align with the central atom \verb|B| along the axis of
the molecule but to project along another axis, as shown in Fig.~\ref{fig:lin1}.

\begin{figure}[ht]
  \centering
  \caption{A linear bend}
  \label{fig:lin1}

  \begin{tikzpicture}
    \node[draw,circle] (A) at (0,0) {A};
    \node[draw,circle] (B) at (2,0) {B};
    \node[draw,circle] (C) at (4,0) {C};
    \node[draw,circle] (D) at (2,2) {D};
    \draw[thick] (A) -- (B) node[midway] (m) {};
    \draw[thick] (B) -- (C) node[midway] (n) {};
    \draw[thick, dashed] (B) -- (D) node[midway] (o) {};
    \path (m) edge [bend left=-90] node[below] {$\theta$} (n);
    \draw[thick, ->] (B) -- (m) node[midway, above] {$\vec{e}_{BA}$};
    \draw[thick, ->] (B) -- (n) node[midway, above right] {$\vec{e}_{BC}$};
    \draw[thick, ->] (B) -- (o) node[near end, right] {$\vec{e}_{a}$};
  \end{tikzpicture}
\end{figure}

The value of the linear bend is computed using Eqn.~\ref{eq:lin1} where
$\vec{e}_a$ is the unit vector in the Cartesian direction of the dummy atom.
Nothing in the code actually checks that it aligns with atom \verb|B|, so the
caller is responsible for making sure this is the case.

\begin{equation}
  \label{eq:lin1}
  \theta = \asin \big( \vec{e}_a \cdot (\vec{e}_{BC} \times \vec{e}_{BA}) \big)
\end{equation}

\subsubsection{Out}
\label{sec:out}

The out-of-plane bend, referred to as \verb|OUT| in the input file, is the angle
between atom \verb|A| and the plane formed by atoms \verb|B|, \verb|C|, and
\verb|D|, as shown in Fig.~\ref{fig:out}.

\begin{figure}[ht]
  \centering
  \caption{An out-of-plane bend}
  \label{fig:out}

  \begin{tikzpicture}
    \node[draw,circle] (A) at (0,1) {A};
    \node[draw,circle] (B) at (2,0) {B};
    \node[draw,circle] (C) at (3,-1.4) {C};
    \node[draw,circle] (D) at (3,1.4) {D};
    \draw[fill=black,triangle path] (B) -- (A) node[midway] (m) {};
    \draw[thick,dashed] (B) -- (0,0) node[midway] (s) {} ;
    \draw[thick] (B) -- (C) node[midway] (n) {};
    \draw[thick] (B) -- (D) node[midway] (o) {};
    \path (m) edge [bend left=-90] node[left] {$\theta$} (s);
    % \draw[thick, dashed] (B) -- (D) node[midway] (o) {};
    % \path (m) edge [bend left=-90] node[below] {$\theta$} (n);
    \draw[thick, ->] (B) -- (m) node[midway, above=.2cm] {$\vec{e}_{BA}$};
    \draw[thick, ->] (B) -- (n) node[midway, above right] {$\vec{e}_{BC}$};
    \draw[thick, ->] (B) -- (o) node[near end, right] {$\vec{e}_{BD}$};
  \end{tikzpicture}
\end{figure}

The value of $\theta$ is computed with the equations below, with the caveat that
if $w_1 + w_2$ is greater than zero, the value of theta is set to $\pi$ with the
sign of $\theta$, minus $\theta$.

\begin{align}
  \vec{v}_5 &= \vec{e}_{BC} \times \vec{e}_{BD} \\
  w_1 &= \vec{e}_{BA} \cdot \vec{e}_{BC} \\
  w_2 &= \vec{e}_{BA} \cdot \vec{e}_{BD} \\
  \phi &= \sin \big( \acos (\vec{e}_{BC} \cdot \vec{e}_{BD}) \big) \\
  \theta &= \asin ( \vec{e}_{BA} \cdot \vec{v}_5 / \phi)
\end{align}

\subsubsection{Torsion}
\label{sec:tors}

The torsional angle, referred to as \verb|TORS| in the input file, is the angle
between the planes formed by the overlapping sets of atoms \verb|A|, \verb|B|,
\verb|C|, and \verb|B|, \verb|C|, \verb|D|, as shown in Fig.~\ref{fig:tors}.
Vectors $\vec{v}_5$ and $\vec{v}_6$ are the vectors normal to the planes $ABC$
and $BCD$, respectively, found by $\vec{e}_{BA} \times \vec{e}_{CB}$ and
$\vec{e}_{DC} \times \vec{e}_{CB}$. To find the angle $\theta$ between these two
normals, and thus between the planes, perform the following transformations:

\begin{align}
  w_2 &= \vec{e}_{BA} \cdot \vec{e}_{CB} \\
  w_3 &= \vec{e}_{DC} \cdot \vec{e}_{CB} \\
  s_2 &= \sqrt{1 - w_2^2} \\
  s_3 &= \sqrt{1 - w_3^2} \\
  w_4 &= \vec{e}_{BA} \cdot \vec{v}_{6} \\
  w_5 &= -\vec{v}_5 \cdot \vec{v}_6 \\
  w &= \frac{w_2}{s_2 s_3} \\
  \theta_0 &= \asin w \\
  \theta &= \begin{cases}
              \theta_0 & w_3 \geq 0 \\
              \pi - \theta_0 & w_3 < 0
            \end{cases}
\end{align}

\begin{figure}[ht]
  \centering
  \caption{A torsion}
  \label{fig:tors}

  \begin{tikzpicture}
    \node[draw,circle] (B) at (0,0) {B};
    \node[draw,circle] (C) at (2,0) {C};
    \node[draw,circle] (D) at (3,-2) {D};
    \node[draw,circle] (A) at (-1,-2) {A};
    \draw[thick] (B) -- (A) node[midway] (m) {};
    \draw[thick] (C) -- (B) node[midway] (n) {};
    \draw[thick] (D) -- (C) node[midway] (o) {};
    \draw[thick, ->] (B) -- (m) node[midway, above left] {$\vec{e}_{BA}$};
    \draw[thick, ->] (C) -- (n) node[midway, above] {$\vec{e}_{CB}$};
    \draw[thick, ->] (D) -- (o) node[midway, above right] {$\vec{e}_{DC}$};
    % vectors
    \draw[thick, ->] (0,-1) -- (0,-0.5) node[midway, right] {$\vec{v_5}$};
    \draw[thick, ->] (2,-1) -- (2,-0.5) node[midway, left] {$\vec{v_6}$};
    % planes
    \draw[dashed] (A) -- (C);
    \draw[dashed] (B) -- (D);

    \draw (n) node [left] {\AxisRotator[x=0.2cm,y=0.25cm,rotate=180]};
    \draw (n) node [left=0.3cm, above=0.25cm] {$\theta$};
  \end{tikzpicture}
\end{figure}

\subsubsection{LINX/LINY}
\label{sec:linxy}

LINX and LINY are the $x$ and $y$ components of the C $\rightarrow$ D unit
vector in the local coordinate system where the B $\rightarrow$ C vector defines
the $+z$ axis and A lies in the $xz$ plane in the $+x$ direction, as shown in
Fig.~\ref{fig:linxy}.

\begin{figure}[ht]
  \centering
  \caption{LINX and LINY}
  \label{fig:linxy}

  \begin{tikzpicture}
    \node[draw,circle] (A) at (1,-2) {A};
    \node[draw,circle] (B) at (0,0) {B};
    \node[draw,circle] (C) at (1,2) {C};
    \node[draw,circle] (D) at (0,4) {D};
    \draw[thick] (B) -- (A) node[midway] (m) {};
    \draw[thick] (C) -- (B) node[midway] (n) {};
    \draw[thick] (D) -- (C) node[midway] (o) {};
    \draw[thick] (D) -- (o) node[midway] (p) {};
    \draw[thick, ->] (B) -- (C) node[midway, right] {$+z$};
    \draw[thick, ->] (C) -- (p) node[midway, above right] {$\vec{e}_{CD}$};
    \draw[thick, ->] (B) -- (2,-1) node[midway, right] {$+x$};
    \draw[dashed] (C) -- (-0,2.5) node[midway, below] { $r_x$ };
    \draw[dashed, ->] (-0,2.5) -- (p) node[midway, above left] { $r_y$ };
  \end{tikzpicture}
\end{figure}

The values are computed using TODO

\subsection{Symmetry-Internal Coordinates}
\label{sec:symm}

With a solid foundation in simple-internal coordinates, symmetry-internal
coordinates (SICs) require much less explanation. SICs are simply linear
combinations of simple-internal coordinates that can be treated as a single
unit. Common examples of SICs include the symmetric stretch in water, which is
the positive combination (sum) of the O-H$_1$ stretch and the O-H$_2$ stretch;
and the anti-symmetric stretch of water, which is the negative combination
(difference) of the two O-H stretches. In the case of water, the third SIC only
has a single component, the simple-internal bending coordinate. INTDER accepts
linear combinations of any number of simple-internal coordinates, but as you may
imagine, the generation of highly-symmetrical SIC systems becomes very
difficult. Describing how to approach such a problem is beyond the scope of this
manual, if not beyond the scope of its author's abilities. Such is the major
weakness of SICs in general.

\subsection{Input Format}
\label{sec:coord-inp}

The listing below shows an example of simple- and symmetry-internal coordinate
input for the formaldehyde (H$_2$CO) molecule, followed by the geometry to help
picture the meaning of these coordinates.

\begin{lstlisting}
  STRE     1    2
  STRE     2    3
  STRE     2    4
  BEND     1    2    3
  BEND     1    2    4
  OUT      1    2    3    4
  1   1   1.000000000
  2   2   1.000000000   3   1.000000000
  3   4   1.000000000   5   1.000000000
  4   2   1.000000000   3  -1.000000000
  5   4   1.000000000   5  -1.000000000
  6   6   1.000000000
  0
  0.000000000        0.000000000       -1.137981497
  0.000000000        0.000000000        1.140677167
  0.000000000        1.771466895        2.235424580
  0.000000000       -1.771466895        2.235424580
\end{lstlisting}

The first section defines the internal coordinates themselves, given in more
descriptive notation below and with atom labels corresponding to
Fig.~\ref{fig:h2co}. This format is straightforward: the name of the coordinate
occurs in the first column, followed by the number of the atom in the Cartesian
geometry that follows in the order described in the previous sections.

\begin{figure}[ht]
  \centering
  \caption{Simple-internal coordinates of formaldehyde}
  \label{fig:h2co}

  \begin{tikzpicture}
    \node[draw,circle] (A) at (0,-1.4) {H$_1$};
    \node[draw,circle] (B) at (2,0) {C};
    \node[draw,circle] (C) at (4,-1.4) {H$_2$};
    \node[draw,circle] (D) at (2,3) {O};
    \draw[thick] (A) -- (B) node[midway] (m) {};
    \draw[thick] (B) -- (C) node[midway] (n) {};
    \draw[thick] (B) -- (D) node[midway] (o) {};
    \path (m) edge [bend left=90] node[left] {$S_4$} (o);
    \path (n) edge [bend left=-90] node[right] {$S_5$} (o);
    \draw[thick, ->] (B) -- (m) node[midway, above left] {$S_2$};
    \draw[thick, ->] (B) -- (n) node[midway, above right] {$S_3$};
    \draw[thick, ->] (B) -- (o) node[near end, left] {$S_1$};

    \draw[dashed] (B) -- (2.7,3) node (x) {};
    \path (x) edge [bend left=-90] node[right] {$S_6$} (D);
  \end{tikzpicture}
\end{figure}

\begin{align}
  S_1 &= r(\text{O}-\text{C}) \\
  S_2 &= r(\text{C}-\text{H}_1) \\
  S_3 &= r(\text{C}-\text{H}_2) \\
  S_4 &= \angle(\text{O}-\text{C}-\text{H}_1) \\
  S_5 &= \angle(\text{O}-\text{C}-\text{H}_2) \\
  S_6 &= OUT(\text{O}-\text{CH}_2)
\end{align}

The second section defines the SICs as linear combinations of the
simple-internals. The first column represents the SIC number, every pair of
following columns represents a simple-internal coordinate and its coefficient.
In practice all of these coefficients are 1.0, so this format is likely to
change in the future. Positive coefficients, such as those for SIC 2 and SIC 3,
are symmetric coordinates like the symmetric stretch for water discussed
earlier. Similarly, negative coefficients, like the second components of SICs 4
and 5, correspond to anti-symmetric coordinates where one simple-internal
coordinate increases while the other decreases. An SIC number of 0 at the start
of the line signals the end of the SIC section.

SICs can also be written algebraically, as shown in the equations below. Note
also the normalization constant that must be applied to give the whole SIC a
magnitude of 1. This constant has the general form $\frac{\sqrt{N}}{N}$, where N
is the number of simple-internal components, although the value for $N=2$ is
typically written as $\frac{1}{\sqrt{2}}$, which does not emphasize this form.

\begin{align}
  L_1 &= r(\text{O}-\text{C}) \\
  L_2 &= \frac{1}{\sqrt{2}}[r(\text{C}-\text{H}_1) + r(\text{C}-\text{H}_1)]\\
  L_2 &= \frac{1}{\sqrt{2}}[\angle(\text{O}-\text{C}-\text{H}_1) + \angle(\text{O}-\text{C}-\text{H}_2)]\\
  L_2 &= \frac{1}{\sqrt{2}}[r(\text{C}-\text{H}_1) - r(\text{C}-\text{H}_1)]\\
  L_2 &= \frac{1}{\sqrt{2}}[\angle(\text{O}-\text{C}-\text{H}_1) - \angle(\text{O}-\text{C}-\text{H}_2)]\\
  L_6 &= OUT(\text{O}-\text{CH}_2)
\end{align}

As a final note, the example input contains exactly the right format for the
Fortran version of INTDER, but the Rust version is much more forgiving with
spacing and alignment. As long as whitespace separates the fields of each line,
the Rust version should parse it correctly.

\section{Displacements}
\label{sec:disp}

The next section of the input file depends on the type of calculation to be run.
The two options are SIC displacements to be converted to Cartesian geometries
and SIC force constants to be converted to Cartesian force constants. This
section is concerned with the former, and the next section covers the latter.

\subsection{Input Format}
\label{sec:disp-inp}

The basic form of displacement input is as shown in the listing below.

\begin{lstlisting}
  DISP 413
  0
  1       -0.0200000000
  0
  1       -0.0150000000
  2       -0.0050000000
  0
  1       -0.0150000000
  3       -0.0050000000
  0
\end{lstlisting}

The Fortran version looks for the number following \verb|DISP| to determine how
many displacements to read, but the Rust version simply looks for \verb|DISP| to
signal to start reading displacements and will continue until the end of the
file. Following this, each displacement is given by zero or more SIC indices
followed by the size of the displacement to take in that SIC. These
displacements are expected to be in \AA{}ngstroms or radians, depending on the
type of coordinate. The end of a single displacement is again signaled by a
\verb|0| at the start of the line. The reason for saying ``zero or more SIC
indices'' before is that an immediate zero (not necessarily immediate in the
\verb|DISP| section, just without preceding SICs), as shown at the top of the
previous listing, corresponds to a zero displacement or equilibrium geometry and
is a valid input.

With that in mind, this listing shows 4 displacements: the zero displacement,
one composed of only a $-$0.02 \AA{} step in SIC 1, a combination of a $-$0.015
\AA{} step in SIC 1 with a $-$0.005 \AA{} step in SIC 2, and a similar
combination of SICs 1 and 3.

\begin{tcolorbox}[title=Tip]
  If you need to verify that the number of displacements in your INTDER input
  file is correct, you can \verb|grep| for these 0 lines:

  \begin{lstlisting}
    $ grep -c `^    0$'
  \end{lstlisting}

  Just remember to subtract 1 for the instance in the SICs! This also assumes
  that the file is formatted as expected by the Fortran version. If you need
  more ``flexible'' formatting, you may need to adapt your regular expression to
  something like

  \begin{lstlisting}
    $ grep -Ec `^\s+0\s*$'
  \end{lstlisting}

  Note also that now we need to pass the \verb|-E| flag to take advantage of
  extended regular expressions that allow \verb|\s|, for example.
\end{tcolorbox}

\subsection{Mathematical Details}
\label{sec:disp-math}

For each of the displacements, $\vec{d}_i$ in the input, the initial set of SIC
values, $\vec{L}_0$, is displaced to yield the desired SICs,
$\vec{L}_d = \vec{L}_0 + \vec{d}_i$. Then, while the absolute value of the
maximum deviation between the current SIC values $\vec{L}_i$ and $\vec{L}_d$ is
greater than 1\e{-14}, the Cartesian coordinates are adjusted by an iterative
process. First, the SIC $\vb B$ matrix is constructed. The corresponding $\vb D$
matrix is just the product of $\vb B$ with its transpose:
$\vb D = \vb B \vb B^\intercal$. Then the $\vb A$ matrix is simply
$\vb A = \vb B^\intercal \vb D^{-1}$. This $\vb A$ matrix is multiplied by the
difference between the desired and current SIC values to yield a step,
$\vec{\delta}$, to be added to the Cartesian coordinates:
$\vec{\delta} = \vb A * (\vec{L}_d - \vec{L}_i)$. Finally, the updated SIC
values, $\vec{L}_{i+1}$, are computed from the resulting Cartesian geometry. As
mentioned above, this process is repeated until convergence is reached or the
maximum number of iterations (currently 20) is reached. While this process
sounds straightforward at this level of abstraction, most of the effort goes
into constructing the $\vb B$ matrix in the first place.

The SIC $\vb B$ matrix (denoted \verb|BS| in the Fortran code and more aptly
\verb|sym_b_matrix| in my Rust code) requires only a fairly simple
transformation (via multiplication by the $\vb U$ matrix) from the
simple-internal $\vb B$ matrix, so most of the effort in this section is
actually focused on the simple-internal coordinates and their $\vb B$ matrix.
The discussion will only return to the construction of $\vb U$ at the very end.

The $\vb B$ matrix is an $N \times M$ matrix, where $N$ corresponds to the
number of simple-internal coordinates, and $M$ is the number of Cartesian
coordinates, or 3 times the number of atoms. Each row of $\vb B$ is the Wilson
$s$-vector for the corresponding simple-internal coordinate. Rather, each row is
conceptually a Wilson $s$-vector, but the actual form differs from that
described by Wilson himself based on later developments in internal coordinate
definitions. Like the coordinates themselves, each coordinate type has its own
$s$-vector formulation and each of these is again described in the following
subsections. Regardless of the specific formulation, the $s$-vectors simply
describe the relationship between the simple-internal coordinates and the
underlying Cartesian coordinates.

\subsubsection{Stretch}
\label{sec:bmat-stre}

\section{Force Constants}
\label{sec:fcs}

\end{document}